---
name: Abilesh Ayyanar
title: "Data Analyst: Cross Selling"
output: html_notebook
---

There are many NA values in the gross income column, so this line removes those rows and puts the new dataset in a file called RealData:
```{r}
RealData <- na.omit(Test)
```

There are many outliers in the age column and in the customer seniority column, so to remove them, some variables must be defined:
```{r}
QAge = quantile(Test$age, probs=c(.25, .75), na.rm =)
QSen = quantile(Test$antiguedad, probs=c(.25, .75), na.rm =)
               
iqrAge <- IQR(Test$age)
iqrSen <- IQR(Test$antiguedad)
```

Create a temporary dataset to hold the values after removing the age outliers:
```{r}
TempDataSet <- subset(RealData, RealData$age > (QAge[1] - 1.5*iqrAge) & RealData$age < (QAge[2]+1.5*iqrAge))
```

Use that dataset as a base and remove all seniority outliers:
```{r}
RealData <- subset(TempDataSet, TempDataSet$antiguedad > (QSen[1] - 1.5*iqrSen) & TempDataSet$antiguedad < (QSen[2]+1.5*iqrSen))
```

You are left with a dataset called RealData that contains no NA values and no outliers in the age and seniority categories.

